Field training 02 - Leaf traits measurements

### 2023-06-13 submission_2/submission_2.qmd
better figure rendering
update tabel, correct LEDA values fig2

---
title: "Field training 02 - Leaf traits measurements"
subtitle: "Documentation"
subsubtitle: "Leaf traits measurements"
author: 
    - "Group 4" 
    - "Denis Streitmatter"
    - "Marie-Louise Korte"
    - "Louis Trinkle"
    - "Maxwell Sivertsen"
    - "Fabian Götz"
    - "Lukas Erzfeld"
date: last-modified
format:
    pdf:
        documentclass: scrreport
        theme: united
        toc: true
        toc-depth: 2
        number-sections: false 
        number-depth: 1
        toc-title: Table of Contents
        toc-location: body
        colorlinks: true
header-includes:  
- \usepackage{graphicx}
- \usepackage{lscape}
- \usepackage{array}
---

@@

# Appendix

<!-- change to landscape -->
\KOMAoptions{paper=landscape,pagesize} 
\recalctypearea

<!-- please feel free to make these tables look prettier-->

| Species | Leaf area (scanner) cm² | Leaf area (camera) cm² | Fresh weight [mg] | Dry weight [mg] | LMA [mg/cm²] scanner | LMA [mg/cm²] camera | EWT [mg/cm²] scanner | EWT [mg/cm²] camera |
|---|---|---|---|---|---|---|---|---|
| Philadelphus Coronarius | 719.97 | 751.19 | 13830 | 2440 | 19.20913371 | 18.41078822 | 0.02 | 0.02 |
| Spirae Chamaedryfolia | 128.27 | 122.26 | 1760 | 620 | 13.72105715 | 14.39555047 | 0.01 | 0.01 |
| Geranium molle | 119.11 | 141.13 | 3590 | 590 | 30.14020653 | 25.43753986 | 0.03 | 0.02 |
| Alliaria petiolata | 810.5 | 892.12 | 17720 | 3630 | 21.8630475 | 19.86279873 | 0.02 | 0.02 |
| Geum urbanum | 184.8 | 194.62 | 2390 | 860 | 12.93290043 | 12.28034118 | 0.01 | 0.01 |
| Ballota nigra | 105.88 | 110.4 | 2090 | 610 | 19.73932754 | 18.93115942 | 0.01 | 0.01 |
| Geranium sanguineum | 82.62 | 97.56 | 1910 | 530 | 23.11788913 | 19.57769578 | 0.02 | 0.01 |
| Acer platanoides | 1142.2 | 1343.79 | 15110 | 4530 | 13.22885659 | 11.24431645 | 0.01 | 0.01 |

: Leaf properties: leaf area, leaf fresh and dry weight, LMA (leaf mass per area) and EWT (equivalent water thickness) {#tbl-data-summary}

@@

| Species | SPAD mean | SPAD stdv | chl Eq. 1 | chl Eq. 2 | chl Eq. 3 | chl Eq. 4 | chl Eq. 5 |
|---|---|---|---|---|---|---|---|
| Philadelphus Coronarius | 47.65 | 1.681434573 | 26.5467675 | 55.53686838 | 54.35018076 | 61.56568402 | 62.75488428 |
| Spirae Chamaedryfolia | 45.6 | 3.215932559 | 24.38084 | 52.23613916 | 50.45974688 | 56.03685716 | 56.72252579 |
| Geranium molle | 36.1 | 3.919183588 | 15.55059 | 38.057711 | 34.49447706 | 36.23261347 | 35.51025089 |
| Alliaria petiolata | 27.64 | 1.416725489 | 9.3583776 | 26.97909046 | 22.96342652 | 24.57293509 | 23.40017292 |
| Geum urbanum | 28.03 | 2.746330886 | 9.6092139 | 27.45774932 | 23.44236855 | 25.01677595 | 23.85444116 |
| Ballota nigra | 38.44 | 4.576558629 | 17.5413216 | 41.37942519 | 38.12070678 | 40.34089174 | 39.8524312 |
| Geranium sanguineum | 48.9 | 6.534332407 | 27.91283 | 57.59152447 | 56.80304051 | 65.20131502 | 66.7438002 |
| Acer platanoides | 31.59 | 5.872998477 | 12.0535811 | 31.97027796 | 28.04602719 | 29.4575616 | 28.43095204 |

: Leaf properties: SPAD measurements and chlorophyll concentration from 5 different equations {#tbl-data-summary}

>>>>

---
title: "Field training 02 - Leaf traits measurements"
subtitle: "Documentation"
subsubtitle: "Leaf traits measurements"
author: | 
    | **Group 4** 
    | Denis Streitmatter 
    | Marie-Louise Korte 
    | Louis Trinkle 
    | Maxwell Sivertsen 
    | Fabian Götz 
    | Lukas Erzfeld
date: last-modified
format:
    pdf:
        documentclass: scrreport
        theme: united
        toc: true
        toc-depth: 2
        number-sections: false 
        number-depth: 1
        toc-title: Table of Contents
        toc-location: body
        colorlinks: true
header-includes:  
- \usepackage{graphicx}
- \usepackage{lscape}
- \usepackage{array}
---

@@

@@

# Appendix
<!-- change to landscape -->
\KOMAoptions{paper=landscape,pagesize} 
\recalctypearea
<!-- please feel free to make these tables look prettier-->
## Table 1: Leaf area and weight
| Species | Leaf area [cm²] scanner | Leaf area [cm²] camera | Fresh weight [mg] | Dry weight [mg] | SLA [cm²/mg] | EWT [mg/cm²] scanner | EWT [mg/cm²] camera |
|---|---|---|---|---|---|---|---|
| Philadelphus Coronarius | 719.97 | 751.19 | 13830 | 2440 | 0.31 | 0.02 | 0.02 |
| Spirae Chamaedryfolia | 128.27 | 122.26 | 1760 | 620 | 0.20 | 0.01 | 0.01 |
| Geranium molle | 119.11 | 141.13 | 3590 | 590 | 0.24 | 0.03 | 0.02 |
| Alliaria petiolata | 810.50 | 892.12 | 17720 | 3630 | 4.07 | 0.02 | 0.02 |
| Geum urbanum | 184.80 | 194.62 | 2390 | 860 | 0.23 | 0.01 | 0.01 |
| Ballota nigra | 105.88 | 110.40 | 2090 | 610 | 0.18 | 0.01 | 0.01 |
| Geranium sanguineum | 82.62 | 97.56 | 1910 | 530 | 5.43 | 0.02 | 0.01 |
| Acer platanoides | 1142.20 | 1343.79 | 15110 | 4530 | 3.37 | 0.01 | 0.01 |

: Leaf properties: leaf area, leaf fresh and dry weight, SLA (surface leaf area) and EWT (equivalent water thickness) {#tbl-data-summary}

## Table 2: Leaf mass per area
| Species | Mean LEDA Database LMA [mg/cm²]  | Leaf mass per area [mg/cm²] scanner | Leaf mass per area [mg/cm²] camera |
|---|---|---|---|
| Philadelphus Coronarius |  | 3.39 | 3.25 |
| Spirae Chamaedryfolia |  | 4.83 | 5.07 |
| Geranium molle | 3.62 | 4.95 | 4.18 |
| Alliaria petiolata | 2.45 | 4.48 | 4.07 |
| Geum urbanum | 2.65 | 4.65 | 4.42 |
| Ballota nigra | 4.71 | 5.76 | 5.53 |
| Geranium sanguineum | 4.58 | 6.41 | 5.43 |
| Acer platanoides | 5.09 | 3.97 | 3.37 |

: LMA (leaf mass per area) from the LEDA database compared to our data {#tbl-data-LMA}

## Table 3: SPAD measurements and chlorophyll
| Species | SPAD mean | SPAD stdv | Chl Eq. 1 | Chl Eq. 2 | Chl Eq. 3 | Chl Eq. 4 | Chl Eq. 5 |
|---|---|---|---|---|---|---|---|
| Philadelphus Coronarius | 47.65 | 1.68 | 26.55 | 55.54 | 54.35 | 61.57 | 62.75 |
| Spirae Chamaedryfolia | 45.6 | 3.22 | 24.38 | 52.24 | 50.46 | 56.04 | 56.72 |
| Geranium molle | 36.1 | 3.92 | 15.55 | 38.06 | 34.49 | 36.23 | 35.51 |
| Alliaria petiolata | 27.64 | 1.42 | 9.36 | 26.98 | 22.96 | 24.57 | 23.40 |
| Geum urbanum | 28.03 | 2.75 | 9.61 | 27.46 | 23.44 | 25.02 | 23.85 |
| Ballota nigra | 38.44 | 4.58 | 17.54 | 41.38 | 38.12 | 40.34 | 39.85 |
| Geranium sanguineum | 48.9 | 6.53 | 27.91 | 57.59 | 56.80 | 65.20 | 66.74 |
| Acer platanoides | 31.59 | 5.87 | 12.05 | 31.97 | 28.05 | 29.46 | 28.43 |

: Leaf properties: SPAD measurements and chlorophyll concentration from 5 different equations {#tbl-data-chl}
